\section{Planning Activities}
\label{sec:plan}

This proposal represents a collaboration that includes \FIXME{9 or 10} senior personnel across \FIXME{4 or 5} institutions. This implies that the coordination effort will be significant, and will not happen without intentionality.  We will initiate the project with in in-person meeting to be held prior to the spring semester for each of the institutions (i.e., right after the beginning of the 2021 calendar year). The purpose of this initial face-to-face meeting will include the following:
\begin{itemize}

\item Ensure that each individual gets to know all other individuals. We will have the PI from each institution give a short (informal) presentation to the rest of the group that both provides background on the strenghts that each institution brings to the table and promotes the general notions that are to be the focus of the research effort.

\item Provide the opportunity for free-form brainstorming. While this planning proposal articulates some of the notions that will be pursued ultimately, given the nature of research the thinking of the participants will surely have evolved. We desire that the planning activities are ultimately targeting our very best research ideas.

\item Identify and provision for the preliminary results that we feel are necessary to credibly make the case that our research ideas are credible. What preliminary work needs to be done, and how will we see that it is accomplished?

\item Finalize the plans for regular meetings, feedback, and ultimate decisions for research direcition.

\end{itemize}

The outcome of this initial face-to-face meeting will include both a near-term plan for further interactions (primarily to be arranged via remote communication) and for action items for each of the participants.