\section{Results from Prior NSF Support}
\label{sec:prior}

Faculty Co-PI C. Ahrens has not had prior NSF funding.
The projects described
below are representative examples of NSF-supported research led by PI 
R.~Chamberlain and the remaining senior personnel.

%\noindent
{\bf CSR: Small: Concurrent Accelerated Data Integration}
{\bf (CNS-1527510,
PI R. Chamberlain, Co-PI R. Cytron)} and
{\bf CSR: Medium: Performant Architecturally Diverse Systems via Aspect Oriented Programming}
{\bf (CNS-1763503, PI R. Chamberlain, Co-PIs J. Buhler and R. Cytron)}, 
10/2015--9/2019 and 9/2018--8/2022, \$519,275 + \$1,214,675. 
%
\textbf{Intellectual Merit} -- This project is investigating the
accelerated execution of streaming applications and data integration workflows, which
increasingly are bottlenecks in data science. Execution platforms
include both graphics engines and FPGAs.
%
\textbf{Broader Impacts} -- This project has supported 5
graduate and 6 REU students.  The applications investigated
come from biology, astrophysics, and the IoT,
further expanding the scope of the students'
experience.
%
\textbf{Evidence of Research Products and their Availability} --
Publications resulting from this work include~\cite{cc19,ccb19,dibs,c17,fcbmc19,mgc16,js16}.
A benchmark suite of the data integration workflows has been released
as a community resource~\cite{dibsv1}.

%\noindent
{\bf CPS: Medium: Collaborative: CyberMech, a Novel Run-Time Substrate for 
Cyber-Mechanical Systems}
{\bf (CNS-1136073 and CNS-1136075,
WU PI C. Gill, Purdue PI S. Dyke)}, 9/2011-8/2016, \$1,800,000 total.  
%
This research project developed novel foundations for parallel real-time computing, demonstrating the first ever real-time hybrid simulation involving a thousand-degree-of-freedom structure at millisecond time scales.
%
\textbf{Intellectual Merit}~-- Results of this research include new methods for parallel real-time execution of control and simulation computations, new parallel real-time scheduling techniques and analyses, and characterization and exploitation of trade-offs involving both high computational demand and stringent timing constraints.
%
\textbf{Broader Impacts}~-- This multi-university project involved 7 PhD, 3 masters, and 7 undergraduate students, and 2 visiting scholars in highly multi-disciplinary research collaborations.  Results of this research are spurring
further advances in parallel real-time computing and natural hazards
engineering.
%
\textbf{Evidence of Research Products and their Availability}~-- Results of
this 
collaborative research appeared in 10 publications at
top-tier conferences and journals.
Data, experiment configurations, platform software, and simulation source-code 
have been published on-line.

\FIXME{RC: need to include projects from Martin and Miriam.}